\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-21 misc2.tex
misc2.c

\begin{alertblock}{Wake/Sleep DSL Induction}
  \textbf{Domain Specific Language (DSL):}
  A finely-tuned program representation, specialized to a domain of programming tasks.
  Prior work in program learning  largely uses hand-engineered DSLs.

@@

\begin{column}{\twocolwid} % The first column within column 2 (column 2.1)

@@

\begin{block}{Why this works: Bootstrapping}

\begin{figure}
\hspace*{-1.5cm}  \begin{tikzpicture}[scale=3,line width=1.5mm]
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $Q$};

    \draw [->] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
    \draw [->] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
    \draw [->] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
%% \begin{itemize}
%% \item Search finds new programs$\implies$ DSL+recognition model get more data
%% \item DSL improves$\implies$easier search, recognition model gets better data
%%   \item Recognition model improves$\implies$ easier search
%%   \end{itemize}

\begin{block}{Generative models of text}
  \begin{figure}
\centering
%\tiny
\tabcolsep=12pt
\begin{tabular}{ccc}\toprule 
\multicolumn{3}{c}{Three Tasks}\\
\hline
1.14531&F&110.9 \\ 
?&CL&163.2 \\
1.29857&F&207.3\\
?&PCFL&143.3 \\\\\midrule 
\multicolumn{3}{c}{Three learned generative models}\\
\hline
 \pop{\scode{?\textbar(1.\textbackslash d+)}}& \pop{\scode{((\textbackslash u\textbackslash u)*)\textbar F}}& \pop{\scode{\textbackslash d\textbackslash d\textbackslash d.\textbackslash d}} \\\\\midrule 
 \multicolumn{3}{c}{Samples from generative models}\\
\hline
1.61&DQDF& 343.8 \\ 
?&F&241.2\\
?&F&647.5\\
1.2&KI&246.8%% \\
%% 1.5080987&F&728.6\\
%% ?&GL&029.3\\
%% 1.453&F&289.1\\
%%     \hline
\\

\midrule \multicolumn{3}{c}{Learned DSL}\\\midrule
\multicolumn{3}{l}{\popp{\scode{$f_1 = $ \textbackslash u\textbackslash w*}}
\hspace{3cm}\popp{\scode{$f_2(x) = $($x$|$f_1$)*}}}\\% $=$ \scode{($x$|\textbackslash u\textbackslash w*)*}}\\
\multicolumn{3}{l}{\popp{\scode{$f_3 = f_2(\scode{`` ''}) = $( \textbar\textbackslash u\textbackslash w*)*}}}\\
\multicolumn{3}{l}{\hspace{1cm}\emph{($f_3$: whitespace delimited words)}}\\
\multicolumn{3}{l}{\popp{$f_4(x) = $ \scode{($x$*$x$)}}\hspace{1cm}\emph{($f_4$: regex `plus')}}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}

\vspace{-0.3cm}
\end{block}
\begin{block}{Learning from Scratch}
  Start w/ McCarthy 1959 Lisp: recursion, conditionals, lists.
  Train on 22 programming exercises.
  After 93 hours on 64 CPUs, rediscovers: \code{map},
  \code{fold}, \code{zip}, \code{unfold}, \code{index}, \code{length}, \code{range}, \code{incr}, \code{decr}.

>>>>

\begin{alertblock}{Wake/Sleep DSL Induction}
  \flushleft
  \textbf{Domain Specific Language (DSL):}
  A finely-tuned program representation, specialized to a domain of programming tasks.
  Prior work in program learning  largely uses hand-engineered DSLs.

@@

\begin{column}{\threecolwid} % The first column within column 2 (column 2.1)

@@
